Realizing temporal graphs from fastest travel times

### 2023-09-22 STACS2023/STACS23-shortversion.tex
Changes of the short version

		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-uToSegmentz2}}}}).

@@

	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.

@@

		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)

@@

			\includegraphics{fig-guess2}}
		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red). 
			\label{fig:FPT-guessG5}}
	\end{subfigure}

	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{1.2\linewidth}{!}{
			%
			\includegraphics{fig-guess3}}
		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
			and guessed the fastest paths of the form
			$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
			and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
			\label{fig:FPT-guessG6}}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{\linewidth}{!}{
			\includegraphics{fig-guess4}}
		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{GG-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
			we
			calculated its corresponding split vertex $v_i \in S_{u,v}$,
			and guessed the fastest paths of the form
			$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
			and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
			\label{fig:FPT-guessG7}}
	\end{subfigure}
	\caption{An example of guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
\end{figure}
%

>>>>

		(see guess~\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}).

@@

	Detailed analysis follows arguing from above (as in \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}) and is deferred to Appendix.

@@

		\caption{Example of an Inner segment guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}), where we guessed the fastest temporal paths of the form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)

@@

			\includegraphics{fig-guess2}}
		\caption{Example of an Inner segment guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}), where we guessed the fastest temporal paths of the form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red). 
			\label{fig:FPT-guessG5}}
	\end{subfigure}

	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{1.2\linewidth}{!}{
			%
			\includegraphics{fig-guess3}}
		\caption{Example of a Split vertex guess I (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}), where, for a fixed vertex $v_i \in S_{u,v}$,
			we calculated its corresponding split vertex $z_j \in S_{w,z}$,
			and guessed the fastest paths of the form
			$v_i \rightarrow v_{i-1} \rightarrow \cdots \rightarrow u \leadsto z \rightarrow z_{r-1} \cdots \rightarrow z_j$ (in blue) 
			and $v_i \rightarrow v_{i+1} \rightarrow \cdots \rightarrow v \leadsto w \rightarrow z_2 \rightarrow \cdots \rightarrow z_{j-1}$ (in red). 
			\label{fig:FPT-guessG6}}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{\linewidth}{!}{
			\includegraphics{fig-guess4}}
		\caption{Example of a Split vertex guess II (\textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}), where, for a vertex of interest $w$, 
			we
			calculated its corresponding split vertex $v_i \in S_{u,v}$,
			and guessed the fastest paths of the form
			$w \leadsto u \rightarrow v_2 \rightarrow \cdots \rightarrow v_i$  (in blue) 
			and $w \leadsto v \rightarrow v_{p-1} \rightarrow \cdots \rightarrow v_{i+1}$ (in red). 
			\label{fig:FPT-guessG7}}
	\end{subfigure}
	\caption{An example of guesses \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT-guessFTPamongv2z2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-uToSegmentz2}}}}, \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromAnotherSegmentAndPaths}}}}, and \textcolor{lipicsGray}{\textsf{\textbf{G-\ref{FPT:guess-splitFromUtoAnotherSegment}}}}.}
\end{figure}
%
